### 2013-09-17 Paper_Markdown.Rmd
Took the bootstrap_wa file and rewrote it for MAT.  Some potential issues remain, partcularly at larger analogue distances, but should be enough to get started with.  Made some minor plotting changes to the paper file.

ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point() + theme_bw()

@@

dissim.scores <- data.frame(dissim = c(min.diss, max.diss),
                            class   = c(rep('Min', length(min.diss)),
                                        rep('Max', length(max.diss))))

ggplot(dissim.scores) + 
  geom_density(aes(x = dissim, fill=class), alpha=0.5) +
  facet_wrap(~class, scales='free') +
  theme_bw()

>>>>

ggplot(data = mds, aes(x = X1, y = X2)) +
  geom_point(alpha=0.5, size = 2) + theme_bw() +
  xlab('MDS Axis One') + ylab('MDS Axis Two') +
    theme(text = element_text(size=24, family='serif'))

@@

dissim.scores <- data.frame(dissim = c(min.diss, max.diss, as.vector(dists)),
                            class   = c(rep('Min', length(min.diss)),
                                        rep('Max', length(max.diss)), rep('Dists', length(as.vector(dists)))))

ggplot(dissim.scores) + 
  geom_density(aes(x = dissim, fill=class), alpha=0.5) +
  #facet_wrap(~class, scales='free') +
  theme_bw() +
  theme(text = element_text(size=24, family='serif'))
